Comparing distance distributions for top predictive features between bins with and without TADs

### 2019-04-22 Scripts/comparing_distance_profiles_using_density_plots.Rmd
added script for evaluating distance profiles using violin and shift plots

```{r}
annotname <- gsub(paste(c("`", 
             "K562", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "K562-Ctcf-Broad_dist")

@@

plottitle <- paste(gsub(paste(c("K562",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "K562-Ctcf-Broad_dist"))

p.K562.10kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

@@

plottitle <- paste(gsub(paste(c("K562",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "K562-Ctcf-Broad_dist"))

p.K562.25kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

@@

plottitle <- paste(gsub(paste(c("K562",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "K562-Ctcf-Broad_dist"))

p.K562.50kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

@@

plottitle <- paste(gsub(paste(c("K562",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "K562-Ctcf-Broad_dist"))

p.K562.100kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcf_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

>>>>

```{r}
annotname <- gsub(paste(c("`", 
             "K562", 
             "-", 
             #"_", 
             #"dist", "count", "perc",
             "Haib", 
             "Sydh",
             "Uta",
             "Uw",
             "Broad",
             "Uchicago"), collapse = "|"), "", "K562-Ctcfc-Broad_dist")

@@

plottitle <- paste(gsub(paste(c("K562",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "K562-Ctcfc-Broad_dist"))

p.K562.10kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcfc_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

@@

plottitle <- paste(gsub(paste(c("K562",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "K562-Ctcfc-Broad_dist"))

p.K562.25kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcfc_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

@@

plottitle <- paste(gsub(paste(c("K562",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "K562-Ctcfc-Broad_dist"))

p.K562.50kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcfc_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```

@@

plottitle <- paste(gsub(paste(c("K562",
                                  "-","_",
                                  "dist","perc","count",
                                  "Haib",
                                  "Sydh",
                                  "Uta",
                                  "Uw",
                                  "Broad",
                                  "Uchicago"), 
                                collapse = "|"), 
                          "",
                          "K562-Ctcfc-Broad_dist"))

p.K562.100kb.ctcf <- ggplot(annotdata.ctcf, aes(x=Ctcfc_dist, color=y)) +
    geom_density() +
    scale_color_discrete(name="Class of\nGenomic Bin",
                         labels=c("Does not overlap\nw/ flanked TAD boundary", "Overlapped w/\nflanked TAD boundary")) +
    ylab("") +
    xlab("") +
    ggtitle("CTCF\nPermutation P-Value: < 0.0001") +
    #annotate("text", x=7, y=.2, label= paste("P-Value:", perm.pval, sep = " "), size=5) +
    theme_bw() +
    theme(axis.text.x = element_text(size=15 #,
                                     #angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     #hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20,
                              hjust=.5))
```
